An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullet Signatures

### 2021-05-07 CMPSpaper_writing/CMPSpaper_writing.Rmd
we don't need to align signatures before extracting cmps

@@

```{r eval=TRUE, echo=FALSE}

lands <- unique(bullets$bulletland)

@@

# dframe <- comparisons %>% select(land1, land2, cmps_score)
# 
# dframe %>% 
#   ggplot(aes(x = land1, y = land2, fill = cmps_score)) +
#   geom_tile() +
#   scale_fill_gradientn(
#     colors=c("darkgrey","darkorange")
#   ) +
#   geom_text(aes(label=cmps_score)) +
#   theme_bw() + 
#   coord_flip()

@@

# comparisons %>%   
#   group_by(bulletA, bulletB) %>% tidyr::nest() %>%
#   mutate(
#     cmps_max_bar = data %>% purrr::map_dbl(
#       .f = function(d) max(compute_average_scores(land1 = d$landA,
#                                                   land2 = d$landB,
#                                                   d$cmps_score)))
#   )

dframe <- comparisons %>% select(-aligned, -cmps)

>>>>

\hh{How about you go into a description of the results from the function `extract\_feature\_cmps`?}

@@

```{r alternative, echo = FALSE}
lands <- unique(bullets$bulletland)

comparisons <- comparisons %>% 
  left_join(bullets %>% select(bulletland, sig1=sigs),
            by = c("land1" = "bulletland")) %>%
  left_join(bullets %>% select(bulletland, sig2=sigs),
            by = c("land2" = "bulletland"))

comparisons <- comparisons %>% mutate(
  cmps = purrr::map2(sig1, sig2, .f = function(x, y) {
    extract_feature_cmps(x$sig, y$sig, include = "full")
    })
)

dframe <- comparisons %>% select(-sig1, -sig2)

dframe$samesource <- with(dframe, bullet_to_land_predict(land1=landA, land2=landB, cmps_score, difference=1))
```

```{r eval=FALSE, echo=FALSE}
lands <- unique(bullets$bulletland)

@@

@@

comparisons0 <- comparisons
dframe0 <- comparisons %>% select(-aligned, -cmps)
